### 2018-05-28 Paper/disc.tex
minor ...

Based on the results presented for a variety of test problems, and a
higher-dimensional chemical kinetics application in this work, it can be said
that the proposed framework seems quite promising in its potential for
identifying favorable scenarios for constructing a reduced-order surrogate in a
computationally efficient manner.  However, it is important to remain cognizant
about the limitations of the framework as well. For instance, it does not
account for the existence of possible correlations between the uncertain
parameters of the model. However, while the assumption of independent
parameters is not always justified, in many cases, correlations between
parameters are not well understood a priori, and assuming mutual independence
could be reasonable at least in an initial screening stage using DGSMs.
Additionally, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition, however,
must anyways be satisfied for the resulting surrogate to be able to represent
the input-output relationship for a given model with reasonable accuracy.
Finally, careful assessment and decision-making is required with regards to
proceeding with the construction of a reduced-order surrogate based on the
outcome of parameter screening, and accuracy of the most-recent full-space
surrogate as well as allocation of computational resources for parameter
screening, and constructing the validation test suite. Implementation to more
advanced applications in the future would enable further development of the
proposed framework.

>>>>

Based on the results presented for a variety of test problems, and a
higher-dimensional chemical kinetics application in this work, it can be said
that the proposed framework seems quite promising in its potential for
identifying favorable scenarios for constructing a reduced-order surrogate in a
computationally efficient manner.  However, it is important to remain cognizant
about the limitations of the framework as well. For instance, it does not
account for the existence of possible correlations between the uncertain
parameters of the model. However, while the assumption of independent
parameters is not always justified, in many cases, correlations between
parameters are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs.
Additionally, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition, however,
must anyways be satisfied for the resulting surrogate to be able to represent
the input-output relationship for a given model with reasonable accuracy.
Finally, careful assessment and decision-making is required with regards to
proceeding with the construction of a reduced-order surrogate based on the
outcome of parameter screening, and accuracy of the most-recent full-space
surrogate as well as allocation of computational resources for parameter
screening, and constructing the validation test suite. Implementation to more
advanced applications in the future would enable further development of the
proposed framework.
